% $Id: TAsubarrays2.tex,v 1.1 2018/09/13 14:07:28 spenton Exp $
\section{Verifying the TA (\tacq{}) Subarrays}\label{sec:subarray}
In this section, we describe the various subarrays used in COS TA.
These subarrays are defined by giving the detector coordinate of the lowest valued corner (C) and the full size (S) for both X and Y.
A subarray is fully specified by giving its XC, XS, YC, and YS. Unless noted, coordinates are in detector coordinates as this is the system in which COS TAs are performed.

TA subarrays are necessary to remove unwanted detector background or spectral or detector features not associated with the target, such as detector
``hot-spots'' or Geocoronal emission (see Penton \& Keyes, 2011). All COS \tacq{} modes use subarrays, but they are different for each mode, detector or detector segment,
and \cenwave{}.  The explanation for the sizes and locations of the TA subarrays are beyond the scope of this ISR, but can be found in the TIR COS-2010-03 (Penton \& Keyes, 2011),
the pre-launch estimates (driven by ray-trace predictions; COS-11-0024A (Penton, 2001), COS-11-0014B (Penton, 2002), \& COS-11-0016A (Penton, 2001) and for
FUV LP2--4 in their respective enabling ISRs.
%(Penton 2018 (LP2), Penton 2018 (LP3) and Penton \& White 2018 (LP4).)
The programs discussed in this ISR do not contain any FUV or NUV spectroscopic \tacq{} exposures, therefore, the bulk of the discussion for the TA subarrays for
spectroscopic TAs are contained in the respective enabling ISRs. The spectroscopic exposures discussed in this ISR will, however, be used to verify
the appropriateness of the XD locations of the subarrays in \S~\ref{subsec:NspVER} (NUV) and \S~\ref{subsec:FspVER} (FUV).

COS TA subarrays are loaded during the HST ground commanding uniquely for each TA exposure.
These are \tacq{} mode, NUV \textit{STRIPE}, \cenwave{}, FUV \textit{SEGMENT} and LP dependent.
Additionally, NUV \tacq{SEARCH} has both imaging and spectroscopic modes, which use different subarrays.
These subarrays change with time in response to detector (e.g., increasing background or ``hot-spots)
or mechanism (e.g., secular OSM drift) monitoring.
There are two stages to the TA verification,
1) ensuring that the intended subarrays were commanded, and
2) that those subarrays were valid for the entire duration of usage.

Ideally, one would compare the commanded subarrays for all exposures to those reported in the {\sf \_rawacq.fits} file.
However, due to FITS conversion issues\footnote{These issues should be addressed for C26 with the corrections outlined in \pr{64849}, \pr{64874}, \& \pr{66840}} with the {\sf \_rawacq.fits} files,
the subarrays verified in this ISR were obtained from the telemetry as reported in the {\sf \_spt.fits} files.

%, \ref{tab:TAnuvSEARCH}, \ref{tab:TAnuvIMAGEpost},
As discussed in \S~\ref{subsec:NUVimSUBS}, tables~\ref{tab:TAnuvIMAGEsmov}--\ref{tab:TAnuvIMAGEmirB} give the TA subarrays for all imaging modes
(\tacq{IMAGE} and \tacq{SEARCH}) as they have evolved since SMOV.
Table~\ref{tab:IMsubs} shows the \tacq{IMAGE} subarrays as reported from the FITS headers during the programs discussed in this ISR.

In \S~\ref{subsec:NUVspSUBS}, table~\ref{tab:NUVspSUBSsad} gives the subarrays for all NUV spectroscopic \tacq{SEARCH} and \texttt{PEAKD} that have executed since SMOV,
and table~\ref{tab:NUVspSUBSxd} gives the subarrays for all NUV \tacq{PEAKXD}s. Table~\ref{tab:NUVspSUBSxd} includes the subarrays used to measure the
calibration lamp XD locations (WCA), as well as the target spectral locations, of all stripes.

In \S~\ref{subsec:FUVspSUBS}, table~\ref{tab:TAsubWCAfuv} gives the subarrays for the WCA portion of all FUV \tacq{PEAKXD}s separated by LP and \cenwave{}.
Table~\ref{tab:FUVsubA} gives the TA subarrays for the SA portion of all FUVA \tacq{}s separated by LP and \cenwave{}.
Table~\ref{tab:FUVsubB} gives the TA subarrays for all LPs and \cenwaves{} for FUVB.
Note that TA has not been enabled for all FUV \cenwaves{}, so only the TA subarrays that are in use are listed.
The FUV tables includes subarrays for all four COS LPs even though only the LP2 and LP3 subarrays were monitored in this ISR.

All verifications indicate that the intended subarrays are being used for all TA exposures. All spectra were visually
inspected to verify that the subarrays would have successfully excluded all known detector hot-spots and the
bright Geocoronal emission lines that can negatively affect TAs.
\subsection{COS NUV Imaging TA subarrays}\label{subsec:NUVimSUBS}
The original (2009) NUV imaging \tacq{IMAGE} and \texttt{SEARCH} TA subarrays are given in Table~\ref{tab:TAnuvIMAGEsmov}.
This table includes entries for the WCA and PSA and both MIRA and MIRB.
The COS FSW uses the same subarrays for the PSA and BOA as the offset on the detector between the aperture locations is small ($\Delta$[AD,XD]$\sim$[11.0,0.4]p).

Due to rising NUV detector background, and supported by an analysis of OSM repeatability, reductions to the SA \tacq{SEARCH}  and
WCA \tacq{IMAGE} subarrays sizes were implemented on 2011.017 (\pr{67139})\footnote{On-orbit OSM position analysis showed that the WCA \fsw{IMCAL} MIRRORA and MIRRORB lamp image
detector locations were fairly repeatable (usually with $\pm$ 50~p AD, and $\pm$ 10~p XD). As discussed in, the WCA TA \tacq{IMAGE} subarrays were reduced by $\pm$ 50~p in XD and $\pm$ 180~p in AD,
and \tacq{SEARCH} subarrays were reduced by 125~p AD and 346~p XD (Penton \& Keyes (2011).}.
During \tacq{IMAGE}, the region of the detector used to determine the source location is small, and is given by the square of the TA parameter \textsc{pcta\_CheckboxSize}, which is currently set to 9$\times$9~p (81 total pixels).
Therefore, no adjustment was warranted for the SA \tacq{IMAGE} subarrays. However, during \tacq{SEARCH}, the counts in the full subarray are used (currently 345$\times$816~p = 19,376~p).
NUV \tacq{SEARCH} TAs are therefore much more vulnerable (by a factor of 3500) to contamination from background events and SAA passages (Penton \& Keyes, 2011).
The updated \tacq{SEARCH} values are given in Table~\ref{tab:TAnuvSEARCH}, and the updated \tacq{IMAGE} subarrays are given in Table~\ref{tab:TAnuvIMAGEpost}.

Due to errors in determining the WCA AD position due to increased NUV detector background, the {\bf \textcolor{GREEN}{bold}} subarrays values were updated on 2014.279 (\pr{78749}).
These changes are given in Table~\ref{tab:TAnuvIMAGEmirB}. Simultaneously, the MIRB \tacq{} lamp exposure time and current settings (for the \plamptwo{} lamp)
were changed from 17s @ LOW current to 12s @ MED current (\pr{78749}). FSW WCA-to-SA offsets (\textsc{[X,Y]imCalTargetOffset}) were adjusted accordingly on 2014.289 (\pr{79116}),
prior to use by HST users on 2014.314. The default exposure time and current for the \plampone{} lamp image ``TAGFLASH''s were changed later with \pr{84463}.

Table~\ref{tab:IMsubs} shows the \tacq{IMAGE} subarrays as reported from the FITS headers during the programs discussed in this ISR.
The MIRB changes outlined in Table~\ref{tab:TAnuvIMAGEmirB} are highlighted, and verified, in the bottom section of this table.
\begin{center}
\begin{deluxetable}{llrrrr}
\tabcolsep 16 pt
%\tabletypesize{\footnotesize}
\tablecolumns{6}
\tablewidth{5.5 in}
\tablecaption{2009--2011.016 \tacq{IMAGE} and \tacq{SEARCH} Subarrays\label{tab:TAnuvIMAGEsmov}.}
\tablehead{\colhead{\textit{APERTURE}}&\colhead{MIRROR}&\colhead{XC}&\colhead{YC}&\colhead{XS}&\colhead{YS}}
\startdata
WCA & MIRA & 268 & 95 & 200 & 660\\
WCA & MIRB & 103 & 361 & 200 & 660\\
PSA or BOA & MIRA & 572 & 108 & 345 & 816\\
PSA or BOA & MIRB & 410 & 200 & 345 & 816
\enddata
\footnotesize
\vspace{-0.5cm}\tablecomments{Updated on 2011.017 due to increased NUV background (\pr{67139}, Penton \& Keyes, 2011). See Table~\ref{tab:TAnuvSEARCH}. }
\normalsize
\end{deluxetable}
\end{center}
\begin{center}
\begin{deluxetable}{llrrrr}
\tabcolsep 16 pt
%\tabletypesize{\footnotesize}
\tablecolumns{6}
\tablewidth{5.5 in}
\tablecaption{2011.017--Present COS \tacq{SEARCH} TA Subarrays\label{tab:TAnuvSEARCH}.}
\tablehead{\colhead{\textit{APERTURE}}&\colhead{MIRROR}&\colhead{XC}&\colhead{YC}&\colhead{XS}&\colhead{YS}}
\startdata
PSA or BOA & MIRA & 630 & 284 & 220 & 470\\
PSA or BOA & MIRB & 469 & 499 & 220 & 470
\enddata
\footnotesize
\vspace{-0.5cm}\tablecomments{Updated on 2011.017 (\pr{67139}, Penton \& Keyes, 2011).}
\normalsize
\end{deluxetable}
\end{center}
\begin{center}
\begin{deluxetable}{llrrrr}
\tabcolsep 16 pt
%\tabletypesize{\footnotesize}
\tablecolumns{6}
\tablewidth{5.5 in}
\tablecaption{2011.017--2014.299 \tacq{IMAGE} Subarrays\label{tab:TAnuvIMAGEpost}.}
\tablehead{\colhead{\textit{APERTURE}}&\colhead{MIRROR}&\colhead{XC}&\colhead{YC}&\colhead{XS}&\colhead{YS}}
\startdata
WCA & MIRA & {\bf \textcolor{GREEN}{345}} & {\bf \textcolor{GREEN}{324}} & {\bf \textcolor{GREEN}{50}} & {\bf \textcolor{GREEN}{300}}\\
WCA & MIRB & {\bf \textcolor{GREEN}{184}} & {\bf \textcolor{GREEN}{539}} & {\bf \textcolor{GREEN}{50}} & {\bf \textcolor{GREEN}{300}}\\
PSA or BOA & MIRA & 572 & 108 & 345 & 816\\
PSA or BOA & MIRB & 410 & 200 & 345 & 816
\enddata
\footnotesize
\vspace{-0.5cm}\tablecomments{{\bf \textcolor{GREEN}{Bold}} values are changes from Table~\ref{tab:TAnuvIMAGEsmov} implemented on 2011.017 (\pr{67139}) due to increased detector background (Penton \& Keyes, 2011). }
\normalsize
\end{deluxetable}
\end{center}
\begin{center}
\begin{deluxetable}{llrrrr}
\tabcolsep 16 pt
%\tabletypesize{\footnotesize}
\tablecolumns{6}
\tablewidth{5.5 in}
\tablecaption{2014.300--Present \tacq{IMAGE} Subarrays\label{tab:TAnuvIMAGEmirB}.}
\tablehead{\colhead{\textit{APERTURE}}&\colhead{MIRROR}&\colhead{XC}&\colhead{YC}&\colhead{XS}&\colhead{YS}}
\startdata
WCA & MIRA & 345 & 324 & 50 & 300\\
WCA & MIRB & {\bf 187} & {\bf 566} & 50 & 300\\
PSA or BOA & MIRA & 572 & 108 & 345 & 816\\
PSA or BOA & MIRB & 410 & 200 & 345 & 816
\enddata
\vspace{-0.5cm}\tablecomments{\footnotesize Due to errors in determining the WCA AD position due to increased NUV detector background, the {\bf \textcolor{GREEN}{bold}} subarrays values were updated on 2014.279 (\pr{78749}).
Simultaneously, the MIRB \tacq{} lamp exposure time and current settings (for the \plamptwo{} lamp)
were changed from 17s @ LOW current to 12s @ MED current (\pr{78749}). FSW WCA-to-SA offsets (\textsc{[X,Y]imCalTargetOffset}) were adjusted accordingly on 2014.289 (\pr{79116}),
prior to use by HST users on 2014.314. The default exposure time and current for the \plampone{} lamp image ``TAGFLASH''s were changed later with \pr{84463}.}
\normalsize
\end{deluxetable}
\end{center}
\input{tamon_ai_table.tex}
