\subsection{C17--C23 COS to SIAF Alignment \label{subsec:siafalign}}

The FGS-to-SI programs provide the opportunity to estimate the co-alignment
of the COS SIAF entry to the actual center of the COS SAs. The FGS-to-SI programs
concludes with two cos \tacq{IMAGE}s and a target that is approximately centered in the COS
aperture. By comparing the [V2,V3] position after the first of these \tacq{IMAGE}s
(the Configuration\#1 or Config\#1 PSA$\times$MIRA \tacq{IMAGE}), a direct comparison is possible.
Table~\ref{tab:fgs2siInit} gives these results for both the Spring and the Fall C17--C23 FGS-to-SI alignment programs.

The columns of Table~\ref{tab:fgs2siInit} are:
\footnotesize
\begin{enumerate}
\item \textit{PROPOSID} gives the HST program id (PID).
\item YEAR.DAY gives the Year and day of the year of the observation.
\item \textit{DATE-OBS} gives the observation date as reported in the
fits header in DY-Mon-YEAR format.
\item gives HST [V2,V3] coordinates (in \arcsec) of
the initial HST pointing before the (Config\#1) PSA$\times$MIRA \tacq{IMAGE}.
\item gives HST [V2,V3] coordinates (in \arcsec) of
the intermediate HST pointing after the (Config\#1) PSA$\times$MIRA \tacq{IMAGE}
and before the (Config\#2) PSA$\times$MIRB \tacq{IMAGE}.
\item gives HST [V2,V3] ``Miss-Distances'' (in \arcsec) of
the initial HST pointing before the (Config\#1) PSA$\times$MIRA \tacq{IMAGE}
and are the Initial Pointing coordinates subtracted from the \textit{LNPSA}
SIAF entry active at the time of the observation.
\item gives HST [V2,V3] ``Miss-Distances'' (in \arcsec) of
the intermediate HST pointing after the PSA$\times$MIRA \tacq{IMAGE}.
\item ``SIAF Dates'' gives the dates the [V2,V3] SIAF entry in the following ``SIAF Entry'' column was active.
\item ``SIAF Entry'' gives the [V2,V3] entries that were active at the time
of the observations of this row.
\end{enumerate}
\normalsize

\input{extrasiaf/colinsiaf.tex}
